---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# lockemetadata

Guidelines and metadata for all Locke Data packages

TODO

* Create CONTRIBUTING.md using [this model](https://github.com/lockedata/datasauRus#contributing-to-the-package)

* Create a set of issues labels. With emojis, and aligning the help wanted one with the one that GitHub recognizes and puts in people' feeds (this repo needs help on blabla issues) DONE

* Use repostatus badges and CRAN badges (one? even more by repo) in all repos.

* Add Locke Data as funder in DESCRIPTION for all packages.

* Create a codemeta.json for each package, and merge them together here.

* Add emojis and the fact that packages are packages in all repo descriptions. DONE

* Add "r", "rstats" and "r-package" as topics for all repo descriptions. DONE

## Find packages

```{r}

repos <- ghrecipes::get_repos("lockedata")
repos <- dplyr::mutate(repos, 
                       name = stringr::str_remove(name,
"lockedata\\/"))
# are packages
repos$is_pkg <- purrr::map_lgl(repos$name,
                               ghrecipes::is_package_repo,
                               owner = "lockedata")

repos <- dplyr::filter(repos, is_pkg, !is_fork)
knitr::kable(repos)


````
